Output Summary

### 2022-09-16 03-post-process/compare-sim-to-obs.Rmd

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output:
   html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base-vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output:
   html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
editor_options: 
  chunk_output_type: console
---

### 2022-09-16 03-post-process/output-plots.Rmd

```{r directories, include = F}
# set root directory to the project directory: one level up from this location
# knitr::opts_knit$set(root.dir = "../")
```

>>>>

```{r directories, include = F}
# set root directory to the project directory: one level up from this location
knitr::opts_knit$set(root.dir = "C:/Users/bstaton/Desktop/Staton/1_critfc/analyses/GR-sslcm/03-post-process")
```
